---
title: "R markdow - How To Import An Excel File"
author: "Faith Kabanda"
date: "2022-07-25"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Extra Notes
 
* *Echo = FALSE* allows you to hide the code.
 
 
* fig.show = “hide”: Hides plots. (leave two trailing spaces/lines to start new line in text)


## R Markdown - Import Excel file


```{r}
library(readxl)
covid_data<- read_excel("C:/Users/Faith Kabanda/OneDrive/Desktop/My Research Work/Vaccines VS Data/covid who data.xlsx", 
    sheet = "Jan 2021", range = "A1:E32")
summary(covid_data$New_cases)
```

## Bloxplts
### Short Notes
* factor(0)
* stat_boxplot creates whiskers
```{r}
library(ggplot2)
new_cases_boxplot<- ggplot(covid_data, aes(x = factor(0), y = New_cases, fill = "red", color = "black")) +stat_boxplot() + geom_boxplot() + xlab("Days Of The Month") + ylab("New Daily Covid 19 Cases") + ggtitle("January 2021 Covid 19 Daily New Cases")
new_cases_boxplot
```

## Scatter Plot
```{r}
library(ggplot2)
new_cases_scatterplot<- ggplot(covid_data, aes(x = Date_reported, y = New_cases)) + geom_point()+ xlab("Days Of The Month") + ylab("New Daily Covid 19 Cases") + ggtitle("January 2021 Covid 19 Daily New Cases")
new_cases_scatterplot
```
## Pie Chart


* If it is stat = "identity" , we are asking R to use the y-value we provide for the dependent variable. If we specify stat = "count" or leave geom_bar() blank, R will count the number of observations based on the x-variable groupings.

* theme_void removes stuff from the background of the data vizualization image.

* under aes, equating*x=""*, creates a pie chart with a complete circle.
```{r}
library(ggplot2) #data vizualization
library(dplyr) #data manipulation
dataset<-data.frame(group = c("Section 1", "Section 2", "Section 3"), value = c(45, 30, 25))
head(dataset)
piechart<- ggplot(dataset, aes( x = "", y = value, fill = group)) + geom_bar(width = 1, stat = "identity", color = "black") + coord_polar("y", start = 0) + geom_col() + geom_text(aes(label = value), position = position_stack(vjust = 0.5)) + theme_void()
piechart
```



